---
title: "This is your first **Quarto** Presentation"
author: "Matteo Chialva & Martino Adamo"
date: "2024-01-24"
format:
  revealjs:
      slideNumber: true
      controls: true
      show-slide-number: print
      incremental: true
      progress: true
      chalkboard: true
embed-resources: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

::: incremental
-   Bullet 1
-   Bullet 2
-   Bullet 3
:::

::: notes
Speaker notes go here.
:::

## Slide with R Output

```{r}
#| echo: true
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

# In the morning

## Getting up

-   Turn off alarm
-   Get out of bed

## Breakfast

-   Eat eggs
-   Drink coffee

## In the evening

# Dinner

-   Eat spaghetti
-   Drink wine

# Going to sleep

-   Get in bed
-   Count sheep
